---
title: "Homework 2"
author: "Ethan_Lamons"
date: "9/5/2020"
output: html_document
---

-----

# Part 2

-----

## part a

__2x + 5y = 33__  
__x + 3y = 19__  


First, convert your system of equations into matrices.
```{r}
a <- matrix(c(2, 1, 5, 3), nrow = 2, ncol = 2)
b <- rbind(33, 19)
c <- matrix(c("x", "y"))
a
b
c
```
Matrix c won't be used to solve this problem, but it is there to show  
that the equation in matrix form will be a*c = b


Next, create the inverse of a, and then multiply the equation by a_inverse
```{r}
a_inverse <- solve(a)
a_inverse
a %*% a_inverse
answer <- a_inverse %*% b
answer
```
Multiplying a_inverse and a gives us the identity matrix as it should, and   
multiplying a_inverse and b gives us our answer as a matrix where x = 4 and  
y = 5.  Proof of these answers is shown below.
```{r}
x <- 4
y <- 5
(2 * x + 5 * y) == 33
(x + 3 * y) == 19

(a %*% answer) == b
```

-----

## part b

The simplest way to do this is to sum the vector and divide by 100.
```{r}
vector_1 <- c(1:100)
vector_1
sum(vector_1) / 100
```

-----

## part c

```{r}
install.packages("dplyr", repos = "http://cran.us.r-project.org")
```

-----

# Part 3

```{r}
row_1 <- c("A", "B", "C", "D")
row_2 <- c("D", "E", "F", "G")
matrix <- rbind(row_1, row_2)
data.frame(matrix)
```

